Untitled

### 2025-03-14 script/r/draft.Rmd
cleanining

>>>>

##Merge internet

```{r}
gg_stack <- readRDS("data/data_rds/gg_stack.rds")
ggg_stack <- readRDS("data/data_rds/ggg_stack.rds")

int_stack <- gg_stack %>%
  left_join(ggg_stack, by = c("iso", "NAME_1", "NAME_2", "NAME_3", "round"))

saveRDS(int_stack, file="data/data_rds/int_stack.rds")

int_stack <- readRDS("data/data_rds/int_stack.rds")

int_stack%<>%
  mutate(pop_adm1= coalesce(pop_adm1.x, pop_adm1.y))%>%
  mutate(pop_adm2 = coalesce(pop_adm2.x, pop_adm2.y))%>%
  mutate(pop_adm3 = coalesce(pop_adm3.x, pop_adm3.y))

int_stack%<>%
  select(-ends_with(".x"), -ends_with(".y"))

data_final %<>%
  left_join(int_stack, by = c("iso", "NAME_1", "NAME_2", "NAME_3", "round"))

countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")

countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE")

data_final%<>%
mutate(gg_region_pot = case_when(
    iso %in% countries_adm1 ~ gg_adm1_pot,
    iso %in%  countries_adm2 ~ gg_adm2_pot, 
    TRUE ~ NA_integer_
  ))%>%
mutate(ggg_region_pot = case_when(
    iso %in% countries_adm1 ~ ggg_adm1_pot,
    iso %in%  countries_adm2 ~ ggg_adm2_pot, 
    TRUE ~ NA_integer_))%>%
  mutate(cvg_region_pot=ifelse(is.na(ggg_region_pot), gg_region_pot, ggg_region_pot))

data_final%<>%
mutate(pop_region = case_when(
    iso %in% countries_adm1 ~ pop_adm1,
    iso %in% countries_adm2 ~ pop_adm2, 
    TRUE ~ NA_integer_
  ))%>%
  mutate(pop_region_log=log(pop_region+1))

data_final%<>%
  group_by(NAME_2) %>%
  mutate(name2_id = cur_group_id()) %>%
  ungroup() %>%
  group_by(NAME_1) %>%
  mutate(name1_id = cur_group_id())%>%
  ungroup()%>%
  mutate(adm1_time = case_when(
    iso %in% countries_adm1 ~ name1_id * 10000 + round,
    TRUE ~ NA_integer_
  ))%>%
mutate(adm1_time = as.integer(as.factor(adm1_time)))%>%
mutate(adm2_time = case_when(
    iso %in% countries_adm2 ~ name2_id * 10000 + round,
    TRUE ~ NA_integer_
  ))%>%
mutate(adm2_time = as.integer(as.factor(adm2_time)))

data_final%<>%
  mutate(country_round=as.numeric(paste0(round,ccode)))%>%
  mutate(region_time = case_when(
    iso %in% countries_adm1 ~ name1_id * 10000 + round, 
    iso %in% countries_adm2 ~ name2_id * 10000 + round,
    TRUE ~ NA_integer_
  ))%>%
  mutate(region_time = as.integer(as.factor(region_time)))

saveRDS(data_final, file="data/data_rds/data_final.rds")
write_dta(data_final, "data/data_dta/data_final.dta")
```
